Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-22 main.tex
:pencil: Add simulation parameters

\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold, Design}
	To characterize the achievable primary-(total-)backscatter rate region of the proposed Metascatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
	\end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	\addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\boldsymbol{p}_k \in \Delta^{M-1},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	% \addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	Problem \eqref{op:weighted_sum_rate} is highly non-convex, and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming and decision threshold designs over the Metascatter-enabled network in Fig. \ref{fi:metascatter_network}.
	The parameters remain fixed unless specified.

	% \begin{table}[t!]
	% 	\centering
	% 	\caption{Parameters in simulation}
	% 	\begin{tabular}{ll}
	% 		Transmit antenna $Q$     & 1   \\
	% 		Tags $K$                 & 2   \\
	% 		States $M$               & 2   \\
	% 		Reflect ratio $\alpha$   & 0.5 \\
	% 		Duration ratio $N$       & 10  \\
	% 		Noise power $\sigma_v^2$ & 1   \\
	% 		Discretization bins      & 256
	% 	\end{tabular}
	% 	\label{ta:parameters}
	% \end{table}
	% Table \ref{ta:parameters} shows the parameters used in simulation.
	% We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
	% For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
	% For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.

>>>>

\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
	To characterize the achievable primary-(total-)backscatter rate region of the proposed Metascatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
	\end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	\addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\boldsymbol{p}_k \in \Delta^{M-1},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	% \addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	Problem \eqref{op:weighted_sum_rate} is highly non-convex, and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk of radius \SI{1}{\meter} centered at the user.
	% The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, the path loss exponents are \num{2.6}, \num{2.4} and \num{2}, while the Ricean factor are \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\SI{36}{\dBm}$.
	All node perform \gls{qam} with $M=2$ input states, the amplitude reflect ratio is $\alpha=0.5$, and the symbol period ratio is $N=20$.
	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \SI{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\SI{70}{\dBm}$ and receive antenna gain \SI{3}{\dBi}.
	All rate regions are averaged over \num{1000} instances.
	% Each node has $M=2$ candidate input states with amplitude reflect ratio $\alpha=0.5$.
	The parameters remain fixed unless otherwise specified.

	\begin{figure}[!t]
		\centering
		\subfloat[Instance 1]{
			\resizebox{0.48\columnwidth}{!}{
				\input{assets/simulation/distribution_weights_1.tex}
			}
		}
		\subfloat[Instance 2]{
			\resizebox{0.48\columnwidth}{!}{
				\input{assets/simulation/distribution_weights_2.tex}
			}
		}
		\caption{Input distribution vs weight $\rho$.}
	\end{figure}

	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{0.8\columnwidth}{!}{
	% 		\input{assets/simulation/distribution_weights.tex}
	% 	}
	% 	\caption{1}
	% 	% \caption{Average primary-(total-)backscatter rate region.}
	% \end{figure}
	% \begin{table}[t!]
	% 	\centering
	% 	\caption{Parameters in simulation}
	% 	\begin{tabular}{ll}
	% 		Transmit antenna $Q$     & 1   \\
	% 		Tags $K$                 & 2   \\
	% 		States $M$               & 2   \\
	% 		Reflect ratio $\alpha$   & 0.5 \\
	% 		Duration ratio $N$       & 10  \\
	% 		Noise power $\sigma_v^2$ & 1   \\
	% 		Discretization bins      & 256
	% 	\end{tabular}
	% 	\label{ta:parameters}
	% \end{table}
	% Table \ref{ta:parameters} shows the parameters used in simulation.
	% We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
	% For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
	% For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
